\newif\ifanonymized
%\anonymizedtrue   % 打开匿名版
\anonymizedfalse    % 打开实名版

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \if\relax\detokenize{#1}\relax
      #2
    \else
      \textbf{#1}: #2
    \fi
    \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3}%
      \if\relax\detokenize{#4}\relax
      \else
        \;$|$\;\textbf{\small #4}%
      \fi
      & \textit{\small #5} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{\raisebox{0.2ex}{\scriptsize$\bullet$}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------Heading-----------------

\begin{center}
  \ifanonymized
    \textbf{\Huge \scshape Anonymous} \\ \vspace{1pt}
    \small
    Anonymous $|$ Anonymous $|$ Anonymous $|$ Anonymous
  \else
    \textbf{\Huge \scshape Austin Jiang} \\ \vspace{1pt}
    \small
    +1 (604) 754-1808 \;$|$\;
    \href{mailto:a68jiang@uwaterloo.ca}{a68jiang@uwaterloo.ca} \;$|$\;
    \href{https://www.linkedin.com/in/austinboyujiang}{linkedin.com/in/austinboyujiang} \;$|$\;
    \href{https://github.com/austinboyujiang}{github.com/austinboyujiang}
  \fi
\end{center}


%-----------Experience-----------------
\section{Experience}
    \resumeSubHeadingListStart
    
    
  \resumeSubheading
    {Noah's Ark Lab, Huawei Canada}{Toronto, ON}
    {Research Intern}{Python, PyTorch}{May 2026 -- Present}
    \resumeItemListStart
        \resumeItem{}{Designed an efficient 3D reconstruction model to reduce token redundancy in Visual Geometry Transformer.}
        \resumeItem{}{Introduced an \textbf{residual-update gating} method for adaptive token early-halt to freeze background computation.}
        \resumeItem{}{Achieved a \textbf{30\% speedup} and \textbf{3\% accuracy boost}, breaking the accuracy-compute Pareto frontier.}
        \resumeItem{}{Built a \textbf{3-stage desensitization training} method to jointly optimize gating layers and fine-tune the backbone.}
    \resumeItemListEnd

  \resumeSubheading
    {Multicore Lab, University of Waterloo}{Waterloo, ON}
    {Undergraduate Research Assistant (Supervised by Dr. Trevor Brown)}{C++, CUDA}{Sep 2025 -- Present}
    \resumeItemListStart
        \resumeItem{}{Developed a unified adapter to support versioned and non-versioned data structures within the benchmark.}
        \resumeItem{}{Benchmarking Version Lib (PPoPP’24) extension with \textbf{10M-key} range queries under \textbf{100+ threads} on GPU.}
        \resumeItem{}{Built \textbf{B+ Tree} and \textbf{ART Tree} against a baseline \textbf{GPU B-Tree} using the GPU Range Query Dictionary library.}
    \resumeItemListEnd
    

\resumeSubheading
    {Wolfram Research}{Remote}
    {Research Intern (Part-time)}{Mathematica}{Sep 2025 -- May 2026}
    \resumeItemListStart
        \resumeItem{}{Developed multi-threaded engine managing \textbf{over 800K} data points across \textbf{8 CPU cores}, achieving \textbf{1.4x speedup}.}
        \resumeItem{}{Developed sparse frontier updates and dense scans, achieving a \textbf{127\% speedup} via load-balancing strategies.}
        \resumeItem{}{Designed a \textbf{benchmark harness} measuring updates per second, active ratio, and scheduling overhead.}
    \resumeItemListEnd

    \vspace{2pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small Research Intern (Part-time)} \;$|$\;\textbf{\small Mathematica} & \textit{\small Sep 2024 -- Jan 2025} \\
    \end{tabular*}\vspace{-5pt}
    \resumeItemListStart
        \resumeItem{}{Developed algorithms to voxelize 3D meshes, detect overhanging regions, increasing infill stability by \textbf{55\%}.}
        \resumeItem{}{Designed \textbf{benchmarking metrics} to measure density, connectivity, and printability of generated infills.}
        \resumeItem{}{Produced a first-author research paper, presented at the \textbf{Wolfram Technology Conference 2025}.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
  


%-----------Projects-----------------
\section{Projects}
  \resumeSubHeadingListStart \setlength{\itemsep}{0.8em}
    \resumeSubItem{\href{https://devpost.com/software/rewrite-2snpat}{Rewrite}, TreeHacks 2026 $|$\;Python}{Built a real-time 3D VR game in Unity that is fully interactive, deploying Hunyuan WorldPlay 1.5 on Modal across 4× H200 GPUs with tensor parallelism (accelerating from 1 fps to 12 fps).
    }

    \resumeSubItem{\href{https://nexhacks2026.vercel.app/}{ADaptiv}, NexHacks 2026 $|$\;Python}{Built a full video object replacement pipeline in ComfyUI, using Gemini for video understanding, Meta SAM3 for pixel-level masking, and Alibaba Wan, accelerated on RTX 4090.
    }
    
    \resumeSubItem{\href{https://github.com/AustinBoyuJiang/LookAround-AI}{LookAround AI}, AdventureX (Multimodal Track Winner) $|$\;Python, React}{Built a voice-controlled multi-agent tour guide using the TEN Framework, integrating Google Maps Street View API for route narration.
    }

    \resumeSubItem{\href{https://austinjiang.com/}{Personal Infrastructure \& Services} $|$\;Linux, FastAPI, SQL}{Built \& maintained a personal Linux server hosting a full-stack website behind Nginx, Cloudflare DNS, cloud storage, OpenVPN, email service, and FastAPI + SQL backends.}
  \resumeSubHeadingListEnd


%-----------Education-----------------
\section{Education}
  \resumeSubHeadingListStart

    % \resumeSubheading
    %   {Carnegie Mellon University}{Pittsburgh, PA}
    %   {BS in Mathematics and Computer Science\;$|$\;Major GPA: 4.0/4.0}{}{Expected Graduation: May 2029}
    %   \smallskip

    \resumeSubheading
      {University of Waterloo}{Waterloo, ON}
      {Bachelor of Computer Science (Honours)\;$|$\;Major GPA: 4.0/4.0}{}{Expected Graduation: Apr 2029}
      \smallskip
      \resumeItemListStart
      \resumeItem{Scholarships}{René Descartes National Scholarship (\$25,000), President’s Scholarship of Distinction (\$2,500)}
      \resumeItem{Coursework}{Data Structures, Algorithms, Development Tools, Linear Algebra}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%--------Skills------------
\section{Skills}
 \resumeSubHeadingListStart
    \resumeSubItem {Languages}{C++, Python, C, Java, Bash, TypeScript, Rust}
    \resumeSubItem {Tools/Libraries}{Pytorch, Linux, Git, CUDA, CMake, Numpy, SQL, Docker, Nginx, Flask, FastAPI}
    \resumeSubItem {Concepts}{
    Transformers,
    Large Language Models,
    Concurrency,
    Compilers,
    Distributed Systems,
    Database
    }
 \resumeSubHeadingListEnd
  
  %-----------Achievements and Awards-----------------
\section{Achievements}
  \resumeSubHeadingListStart
    \resumeSubItem {Canadian Computing Olympiad 2026}
      {Authored Day 1 Problem 3 (Contestant average score: 0.7/25).}
    \resumeSubItem {Discover Citadel Program}
      {Invited as 1 of $\sim$100 students ($<1\%$ acceptance rate).}
    \resumeSubItem {Jane Street First-Year Trading and Technology Program}
      {Invited as 1 of $\sim$100 students ($<1\%$ acceptance rate).}
    \resumeSubItem {Generation Google Scholarship}
      {Google's flagship global undergrad scholarship for impact in technology (1 of 55).}
    \resumeSubItem {Canadian Computing Olympiad \href{https://cemc.uwaterloo.ca/sites/default/files/documents/2024/2024CCOResults.pdf}{2024} \& \href{https://cemc.uwaterloo.ca/sites/default/files/documents/2025/cco_summary.pdf}{2025}}
      {Silver medalist x2 (5th and 6th out of 10,000+ participants).}
    \resumeSubItem {USACO 2024 (Platinum)} {Achieved the highest division, ranked top 100 out of 15,564 participants.}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
